---
title: "Map"
author: "Caroline Lisevski"
date: "9/10/2020"
output: html_document
---

## Creating an interactive map on R Markdown using `leaflet` package

In this work we are going to plot an interactive map from the restaurants in Paris. The data was obtained in https://www.kaggle.com/svrcek/paris-restaurants.

```{r}
library(leaflet)
library(dplyr)
library(tidyverse)
library(tidyr)
set.seed(1986)
rest.paris <- read.csv2("restaurants-casvp.csv")
head(rest.paris)
```

From this data set, we will keep the columns with the restaurant's name (`Nom.restaurant`) and the latitude and longitude coordinates (`tt`). We will also split the column `tt` into two, separating latitude from longitude coordinates.

```{r}
rest.paris <- rest.paris %>% select("Nom.restaurant", "tt")
colnames(rest.paris) <- c("Restaurant", "tt")
rest.paris <- rest.paris[complete.cases(rest.paris),]
rest.paris <- separate(rest.paris, col = tt, into = c("Latitude","Longitude"), sep = ",")
rest.paris$Latitude <- as.numeric(rest.paris$Latitude)
rest.paris$Longitude <- as.numeric(rest.paris$Longitude)
head(rest.paris)
```

Now we are going to plot the interactive map using the data from the data frame above.

```{r}
rest.map <- rest.paris %>% leaflet() %>% addTiles() %>% 
        setView(lat = 48.85, lng = 2.35, zoom = 12) %>%
        addMarkers(lat = rest.paris$Latitude, lng = rest.paris$Longitude, 
                   popup = rest.paris$Restaurant)
rest.map
```




