---
title: 'Shiny Presentation:'
subtitle: 'Simulating the Probability of a ten-faced die rolled n times'
author: "Caroline Lisevski"
date: "9/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(ggplot2)
```

## The Project

This project is the final project from Developing Data Products course and the main objective is to write a Shiny application.

Here it was built an application simulating the probability of a ten-faced die rolled n times.

## How to include R code embedded on a slide

The following code calculates the probability of a ten-faced die rolled n times.

```{r, eval=FALSE}
set.seed(1986)
n <- 5000
die <- 1:10
vec.n <- n
sum.n <- n
 r <- 1
for(i in 1:vec.n){
      vec.n[i] <- roll <- sample(die, size = 1, replace = TRUE)
      sum.n[i] <- sum(vec.n[1:i]==r)/i
}
```







## Probability when n = 10000

```{r, echo = FALSE}
set.seed(1986)
n <- 5000
die <- 1:10
vec.n <- n
sum.n <- n
 r <- 1
for(i in 1:vec.n){
      vec.n[i] <- roll <- sample(die, size = 1, replace = TRUE)
      sum.n[i] <- sum(vec.n[1:i]==r)/i
}
 
 df <- cbind.data.frame(number = 1:n, sum.n)
 ggplot(df, aes(x = number, y = sum.n)) + geom_point(color = "magenta") +
         geom_hline(yintercept = 1/10, color = "blue")
 
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

